% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\setlength{\textheight}{9.5in} % increase text height to fit on 1-page
%\usepackage[hmargin=2.5cm,vmargin=0.2cm]{geometry}
\begin{document}


\address{\large\bf  Anthony Gentile}
\address{Matthews, NC \\  asgentile@gmail.com}

\begin{resume}

\section{EDUCATION}
    University of Washington, Seattle, WA  \\
    Master of Science in Computational Linguistics, December 2013

    Appalachian State University, Boone, NC  \\
    Bachelor of Science in Business Administration, Summer 2008   \\
    Concentration in Computer Information Systems       \\
    Minor in German  \\
    Cum Laude

\section{EXPERIENCE}
   \vspace{-0.1in}
   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Engineering Team Lead} \>Follow Up Boss     \> February 2014 - Present\\
                             \>San Francisco, CA (Remote)
   \end{tabbing}\vspace{-5pt}      % suppress blank line after tabbing
   \begin{itemize}
    \item Lead engineering team through development cycles.
    \item Coordinate efforts and improve overall productivity of the engineering team.
    \item Identify and address key engineering needs in infrastructure and systems.
    \item Architect and assist in implementation of critical services and features.
    \item Helping choose key technologies for the future of the product.
    \item Hiring and onboarding engineers.
    \item Supporting customers directly, ensure they are happy and our product is solving their problems.
    \item Implemented large scale email processing service which to date has processed over 1.2 billion emails.
   \end{itemize}

   \begin{tabbing}
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
    {\bf Owner} \>AG Technology Solutions, LLC     \> August 2010 - Present\\
                             \>Charlotte, NC
   \end{tabbing}\vspace{-5pt}      % suppress blank line after tabbing
    Providing web application development and scalability consulting services to existing large scale websites and startups. Clients have included Follow Up Boss, Audiomack, Maker's Row, Instatrade, GroundSwell.FM, TotallyHer, and more.

   \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
   {\bf Web Engineer}  \>OmniTI \> July 2008 - May 2011\\
                          \>Brooklyn, NY
   \end{tabbing}\vspace{-5pt}
   \begin{itemize}
    \item Performed web performance analysis for a large ISP portal application. This included load testing, code profiling using XHProf and an analysis of the common front-end performance pitfalls.
    \item Main developer for 3.4 million+ user teen social network, TeenSpot. Providing new features for the site while focusing on performance and security. Responding to security issues and improving existing security within the code base using best practices.
    \item Helped create a business intelligence tool and implemented security code changes for Etsy, a large e-commerce site specializing in user-made goods. These changes included better password storage using adaptive hashing and dynamic salts, stronger password reset tokens, rate limiting on login forms, and moving the administration panel to a web server accessible only through the VPN.
    \item Main developer for an in house PHP security auditing tool. This application analyzes PHP opcodes and provides static analysis to better assist security auditors in finding weaknesses within PHP code bases.
    \item Implemented SQL Server compatibility within WordPress. This patch provides on-the-fly SQL dialect translations while maintaining PHP 4 compatibility and full feature support. Also tested for the top twenty most popular WordPress plugins. This patch was displayed by Microsoft at their PDC conference to show their open source compatibility with PHP and SQL Azure.
    \item Helped build a custom, scalable content management system for AlliSports, a large sports event website.
    \item Assisted in several PHP security audits.
    \end{itemize}

    \begin{tabbing}%
   \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
   {\bf Partner}  \>Redlink Technology Solutions LLP \> October 2007 - July 2008\\
                          \>Boone, NC
   \end{tabbing}\vspace{-10pt}
    Founded during college as a company specializing in web-based e-commerce solutions for small businesses.

\section{TECHNICAL KEYWORDS}

    HTML5, XHTML, CSS3, LESS, Sass, React, Styled Components, Backbone, jQuery \\
    PHP, Python, JavaScript \\
    PostgreSQL, MySQL, Redis, Memcached, SQL Server, SQLite, MongoDB, RabbitMQ \\
    Amazon Web Services, UNIX, Apache, SSH, StatsD, Monit, ElasticSearch, Varnish, HAProxy \\
    Docker, Vagrant, Ansible, Chef, Terraform, Git, MVC Frameworks, Test-Driven Development, Agile, Scrum


\section{CERTIFICATIONS}
    Certified Scrum Master - (Credential ID: 562293) \\
    Zend Certified Engineer - (PHP5, CandidateID: ZEND010529) \\
    Network+

\end{resume}
\end{document}
